Notes on Semi-Supervised `Novelty Detection'

### 2011-04-28 semisupervised/notes.tex
some changes

As expected, having perfect information of the distributions $P(x|c \in known)$ and $P(x)$
allows us to build an optimal detector as seen on \autoref{fig:dora-data-perfect}.

@@

The room categories where $P(x|k)$ threshold gave worst results were:
Computer Lab, Conference Hall, Meeting Room and Robot Lab.

These are 
\begin{figure}
\missingfigure[figwidth=\textwidth]{}
\caption{\label{fig:confusion-matrix-dora}Confusion matrix for the 11 classes that make up the dora distribution.}
\end{figure}

>>>>

Having perfect information of the distributions $P(x|c \in known)$ and $P(x)$
allows us to build an optimal detector as seen on \autoref{fig:dora-data-perfect}.

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{dora-data/classification.pdf}
\caption{\label{fig:confusion-matrix-dora}
         Confusion matrix for the 11 classes that make up the dora distribution.}
\end{figure}
